Reanalysis Step 5: Main Effects Outcome Analysis

### 2025-08-31 reanalysis-5-outcome_analysis.qmd
fix

```{r marginal-effects}
# Check if AMEs are cached
ame_cache_file <- file.path(reanalysis_data_dir, "ame_results_main_effects.rds")
force_recalc_ame <- TRUE  # Set to TRUE to force recalculation

@@

# Extract estimates and SEs for pooling
ame_estimates <- sapply(ame_list, function(x) x$estimate)
ame_ses <- sapply(ame_list, function(x) x$std.error)

>>>>

```{r marginal-effects}
# Check if AMEs are cached
ame_cache_file <- file.path(reanalysis_data_dir, "ame_results_main_effects.rds")
force_recalc_ame <- FALSE  # Set to TRUE to force recalculation

@@

# Extract estimates and SEs for pooling
# avg_comparisons returns a data frame, so we need to extract the first row
ame_estimates <- sapply(ame_list, function(x) {
  if (is.data.frame(x)) {
    x$estimate[1]
  } else {
    x$estimate
  }
})

ame_ses <- sapply(ame_list, function(x) {
  if (is.data.frame(x)) {
    x$std.error[1]
  } else {
    x$std.error
  }
})
